% Created 2016-09-10 Sat 12:08
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{hyperref}
\tolerance=1000
\author{Daniel Dyla}
\date{\today}
\title{CSE 361 HW-0}
\hypersetup{
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 24.5.1 (Org mode 8.2.10)}}
\begin{document}

\maketitle

\section{1.2-1}
\label{sec-1}

Give an example of an application that requires algorithmic content at
the application level, and discuss the function of the algorithms
involved.


An application that manages students for a classroom might require
algorithmic content at the application level. It could use a sorting
algorithm to sort students alphabetically by name for attendance, or a
random shuffling algorithm in order to assign random seats to the
students in the class.

\section{1.2-2}
\label{sec-2}

Suppose we are comparing implementations of insertion sort and merge
sort on the same machine. For inputs of size n, insertion sort runs in
$8n^2$ steps, while merge sort runs in $64 n \lg n$ steps. For which
values of n does insertion sort beat merge sort?


Insertion sort beats merge sort when $2 <= n <= 6$ (where n is an
integer)

\section{1.2-3}
\label{sec-3}

3 What is the smallest value of n such that an algorithm whose running
time is $100n^2$ runs faster than an algorithm whose running time is
$2^n$ on the same machine?


Assuming n can ony be an integer, the smallest value of n where
$100n^2$ is faster than $2^n$ is 15.

\section{Table of values}
\label{sec-4}

\begin{center}
\begin{tabular}{lrrrrrrr}
 & 1 second & 1 minute & 1 hour & 1 day & 1 month & 1 year & 1 century\\
\hline
lg(n) & e$^{\text{1e6}}$ & e$^{\text{60e6}}$ & e$^{\text{3.6e9}}$ & e$^{\text{86.4e9}}$ & e$^{\text{2.59e12}}$ & e$^{\text{946e12}}$ & e$^{\text{94.6e15}}$\\
sqrt(n) & 1\,(12) & 3.6\,(15) & 12.0\,(18) & 7.46\,(21) & 6.72\,(24) & 895\,(27) & 8.95\,(33)\\
n & 1\,(6) & 60\,(6) & 3.60\,(9) & 86.4\,(9) & 2.59\,(12) & 946\,(12) & 94.6\,(15)\\
n lg n & 87.8\,(3) & 3.95\,(6) & 189\,(6) & 3.91\,(9) & 102\,(9) & 30.5\,(12) & 2.66\,(15)\\
n$^{\text{2}}$ & 1000 & 7746 & 60\,(3) & 294\,(3) & 1.61\,(6) & 30.7\,(6) & 307\,(6)\\
n$^{\text{3}}$ & 100 & 391 & 1532 & 4420 & 13700 & 98\,(3) & 455\,(3)\\
2$^{\text{n}}$ & 19 & 25 & 31 & 36 & 41 & 49 & 56\\
n! & 9 & 11 & 12 & 14 & 15 & 17 & 18\\
\end{tabular}
\end{center}
% Emacs 24.5.1 (Org mode 8.2.10)
\end{document}
